Capturing Policies for BYOD

### 2016-11-17 paper.tex
switched to llncs and some trivial things

\documentclass{easychair}

@@

@@

\begin{abstract}
  % 4 Sentences
  BYOD policies are informally specified using natural language.
  Various tools and \ac{MDM} solutions can implement parts of the policies, but there isn't a means to tie the written policy to its enforcement method.
  In this paper we show how AppPAL can be used to capture policies for BYOD.
  We identify common BYOD idioms and delegation structures.
\end{abstract}

@@

This paper describes a formalization of five BYOD policies using AppPAL---a policy language for mobile device privacy preferences~\cite{hallett_apppal_2016}.
Using our formalization we identify the common concerns and trust relationships in these policies.
We show how AppPAL can be used to implement these policies, and describe precisely the different trust relationships.
AppPAL is an instantiation of the SecPAL authorization language~\cite{becker_secpal:_2010} for mobile device policies.
We have found, however, that it is a good fit for other policies surround the mobile ecosystem as well~\cite{hallett_specifying_2016}.
Using these papers we identify a set of standard decisions and trust relationships used in BYOD policies.
These are BYOD idioms that are capture decisions at common requirements in BYOD policies.
These give a guide for where future work implementing BYOD tools should focus their efforts to cover more aspects of policies.

@@

Our approach does not try to implement the policy.
Rather we attempt to capture the goals of the policy rule so that the delegations of trust, tools used, and their configuration is made explicit.
This gives us greater clarity as to which tool is being trusted to implement what policy.
It allows us to see who is being trusted to make which decisions.
It also lets us use automatic tools to uncover aspects of the policy that may be unimplemented~\cite{hallett_specifying_2016}.
Continuing with the example above, this can be expressed in AppPAL as:

@@

\todo{%
  Why is the AppPAL better?
  Clearer, explicit, can identify problems automatically.

@@

\subsection{Changes to AppPAL}

In order to describe BYOD specific conditions we instantiate AppPAL with four kinds of facts: \emph{can, has, is} and \emph{must}.
Like other SecPAL-based instantiations~\cite{becker_framework_2009,aziz_secpal4dsa:_2011} we extend the syntax of facts to support these constructs.
Internally, however, they are treated as standard predicates.

@@

When using AppPAL to describe policies, we also need to describe what domain each variable belongs to.
This is performed through the \emph{is}-kind facts.
AppPAL inherits from SecPAL (and Datalog) a safety condition that all variables in the head of an assertion must be referenced in the body.
This leads to policies which can be noisy to read.
For example in the SANS policy there is a rule that states that devices can only connect to wireless access points owned by the company.
This is written in AppPAL as:
\begin{lstlisting}
'company' says Device canConnectToAP(AP)
  if AP isOwnedByCompany,
     Device isDevice,
     AP isAccessPoint.
\end{lstlisting}
To simplify the presentation we allow a special sugared notation for conditionals expressing the type of a variable (\emph{variable \emph{is}Type}).
Any variable in the head of the rule of the form \texttt{\emph{Type}:Variable} is replaced by the variable and a conditional that \texttt{Variable is\emph{Type}} is added to the body.
The rule can be re-written as shown bellow hiding the typing statements.
\begin{lstlisting}
'company' says Device:D canConnectToAP(AP:X)
  if X isOwnedByCompany.
\end{lstlisting}

@@

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices.
Companies are expected to modify the document to suit their needs.
The policy is general; not specific to any particular industry, device, or country's legislation.
The second is taken from Healthcare Information Management System Society~\cite{healthcare_information_and_management_systems_society_mobile_2012};
  a US non-profit company trying to improve healthcare through IT.
It is relatively short but interesting because it contains concerns specific to healthcare scenarios, and is written as a contract the users are agreeing to follow.
In contrast every other policy we looked at is written as a series of rules users should follow to ensure compliance.
The policy is designed as a sample agreement for a system trying to manage personal mobile devices in a healthcare environment.
The third is taken from an British hospital trust~\cite{kennington_mobiles_2014}, and describes the BYOD scheme used in practice at the hospital.
Finally two simpler policies are taken from Edinburgh university~\cite{david_williamson_bring_2015} and a company specialising in emergency sirens~\cite{code3pse.org_sample_????}.
These policies are simpler than the other comprised of much more general rules and only a page or two in length.

@@

The policies are summarised in \autoref{tab:summary}.
Each policy contains a series of \emph{rules}, which are implemented by one or more \emph{AppPAL assertions}.
The \emph{policy coverage} represents the number of rules that have an AppPAL description attached.

Not all the rules in a policy require an AppPAL translation.
For example rule 9.1 in the NHS policy states:
\begin{policyrule}{NHS}
  Downloading of personal apps onto a corporately issued mobile device should be avoided where possible.
  The Trust would not encourage staff members to download apps for personal use onto a corporately issued mobile device.
  All staff are reminded that they must adhere to the guidance outlined in the Social Media Policy.
\end{policyrule}
The rule does not prohibit any action, and doesn't require the staff to do anything different.
It does remind staff to be aware of a rule which we could implement with an acknowledgement; a statement that the party has acknowledged a rule.
\begin{lstlisting}
'nhs-trust' says Staff:S mustAcknowledge('avoid-installing-personal-apps').
'nhs-trust' says Staff:S mustAcknowledge('social-media-policy').
\end{lstlisting}
In this case, however, since nothing is required even an acknowledgement seems excessive.

@@

  \newcommand{\angledtitle}[1]{\rlap{\rotatebox{30}{#1}}}

@@

  \caption{Summary of AppPAL facts used in multiple BYOD policies.}

@@

\todo{Provide a template for what kinds of policy should be implemented like this and template AppPAL.}

@@

AppPAL requires all assertions be made by an explicit speaker.
When translating the policies the author of the policy is generally used as the speaker of the rule (\autoref{tab:principals}),
  with the exception of the HiMSS policy that is written as a contract the user is agreeing to.
All the policies delegate also describe other entities that might also make assertions.
With AppPAL policies any speaker can delegate a decision to another speaker (with restrictions on re-delegation).
This might be to a user to acknowledge a policy, or it might be to other groups in the company who are responsible for certain decisions.

@@

Armando~\etal~developed BYODroid as a tool for enforcing BYOD policies through a secure marketplace~\cite{armando_enabling_2014}.
Their tool allows companies to distribute a secure app~store where through a combination of static and dynamic tools they can verify that apps follow fine-grained permission policies.
Their policies are low level, based on ConSpec~\cite{aktug_conspec_2008}, allowing checks based on the JVM state.
Using their tool they implemented parts of a policy relating to personal networks, and data management for the NATO Communications and Information Agency~\cite{armando_developing_2016}.
Their work shows how parts of a BYOD policy can be checked for and enforced using tools.
An AppPAL policy might use BYODroid to ensure that a parts of a policy are enforced (as well as other tools for other parts).
AppPAL makes explicit how the natural language policy is implemented and by which tools.

>>>>

\documentclass{llncs}

@@

\newcommand{\AppPAL}[0]{SecPAL4BYOD}

@@

\begin{abstract}
  % 4 Sentences
  BYOD policies are informally specified using natural language.
  Various tools and \ac{MDM} solutions can implement parts of the policies, but there isn't a means to tie the written policy to its enforcement method.
  In this paper we show how \AppPAL~can be used to capture policies for BYOD.
  We identify common BYOD idioms and delegation structures.
\end{abstract}

@@

This paper describes a formalization of five BYOD policies using a variation of SecPAL called \AppPAL.
This has been implemented atop of AppPAL---a policy language for mobile device privacy preferences~\cite{hallett_apppal_2016}.
Using our formalization we identify the common concerns and trust relationships in these policies.
We show how \AppPAL\AppPALcan be used to implement these policies, and describe precisely the different trust relationships.
\AppPAL\AppPALis an instantiation of the SecPAL authorization language~\cite{becker_secpal:_2010} for mobile device policies.
We have found, however, that it is a good fit for other policies surround the mobile ecosystem as well~\cite{hallett_specifying_2016}.
Using these papers we identify a set of standard decisions and trust relationships used in BYOD policies.
These are BYOD idioms that are capture decisions at common requirements in BYOD policies.
These give a guide for where future work implementing BYOD tools should focus their efforts to cover more aspects of policies.

@@

Our approach does not try to implement the policy.
Rather we attempt to capture the goals of the policy rule so that the delegations of trust, tools used, and their configuration is made explicit.
This gives us greater clarity as to which tool is being trusted to implement what policy.
It allows us to see who is being trusted to make which decisions.
It also lets us use automatic tools to uncover aspects of the policy that may be unimplemented~\cite{hallett_specifying_2016}.
Continuing with the example above, this can be expressed in \AppPAL~as:

@@

\todo{%
  Why is the \AppPAL~better?
  Clearer, explicit, can identify problems automatically.

@@

\subsection{Changes to \AppPAL}

In order to describe BYOD specific conditions we instantiate \AppPAL~with four kinds of facts: \emph{can, has, is} and \emph{must}.
Like other SecPAL-based instantiations~\cite{becker_framework_2009,aziz_secpal4dsa:_2011} we extend the syntax of facts to support these constructs.
Internally, however, they are treated as standard predicates.

@@

When using \AppPAL~to describe policies, we also need to describe what domain each variable belongs to.
This is performed through the \emph{is}-kind facts.
\AppPAL~inherits from SecPAL (and Datalog) a safety condition that all variables in the head of an assertion must be referenced in the body.
This leads to policies which can be noisy to read.
For example in the SANS policy there is a rule that states that devices can only connect to wireless access points owned by the company.
This is written in \AppPAL~as:
\begin{lstlisting}
'company' says Device canConnectToAP(AP)
  if AP isOwnedByCompany,
     Device isDevice,
     AP isAccessPoint.
\end{lstlisting}
To simplify the presentation we allow a special sugared notation for conditionals expressing the type of a variable (\emph{variable \emph{is}Type}).
Any variable in the head of the rule of the form \texttt{\emph{Type}:Variable} is replaced by the variable and a conditional that \texttt{Variable is\emph{Type}} is added to the body.
The rule can be re-written as shown bellow hiding the typing statements.
\begin{lstlisting}
'company' says Device:D canConnectToAP(AP:X)
  if X isOwnedByCompany.
\end{lstlisting}

@@

We analysed five different policies to find common idioms.
The first is the \emph{Security Policy Template: Use of Handheld Devices in a Corporate Environment}, published by the SANS Institute~\cite{nicholas_r._c._guerin_security_2008}.
This is a hypothetical policy published to help companies mitigate the threats to corporate assets caused by mobile devices.
Companies are expected to modify the document to suit their needs.
The policy is general; not specific to any particular industry, device, or country's legislation.
The second is taken from Healthcare Information Management System Society~\cite{healthcare_information_and_management_systems_society_mobile_2012};
  a US non-profit company trying to improve healthcare through IT.
It is relatively short but interesting because it contains concerns specific to healthcare scenarios, and is written as a contract the users are agreeing to follow.
In contrast every other policy we looked at is written as a series of rules users should follow to ensure compliance.
The policy is designed as a sample agreement for a system trying to manage personal mobile devices in a healthcare environment.
The third is taken from an British hospital trust~\cite{kennington_mobiles_2014}, and describes the BYOD scheme used in practice at the hospital.
Finally two simpler policies are taken from The University of Edinburgh~\cite{david_williamson_bring_2015} and a company specialising in emergency sirens~\cite{code3pse.org_sample_????}.
These policies are simpler than the other comprised of much more general rules and only a page or two in length.

@@

The policies are summarised in \autoref{tab:summary}.
Each policy contains a series of \emph{rules}, which are implemented by one or more \emph{\AppPAL~assertions}.
The \emph{policy coverage} represents the number of rules that have a \AppPAL~description attached.

Not all the rules in a policy require a \AppPAL~translation.
For example rule 9.1 in the NHS policy states:
\begin{policyrule}{NHS}
  Downloading of personal apps onto a corporately issued mobile device should be avoided where possible.
  The Trust would not encourage staff members to download apps for personal use onto a corporately issued mobile device.
  All staff are reminded that they must adhere to the guidance outlined in the Social Media Policy.
\end{policyrule}
The rule does not prohibit any action, and doesn't require the staff to do anything different.
It does remind staff to be aware of a rule which we could implement with an acknowledgement; a statement that the party has acknowledged a rule.
\begin{lstlisting}
'nhs-trust' says Staff:S mustAcknowledge('avoid-installing-personal-apps').
'nhs-trust' says Staff:S mustAcknowledge('social-media-policy').
\end{lstlisting}
In this case, however, since nothing is required even an acknowledgement seems excessive.

@@

  \newcommand{\angledtitle}[1]{\rlap{\rotatebox{45}{#1}}\hspace{1em}}

@@

  \caption{Summary of \AppPAL~facts used in multiple BYOD policies.}

@@

\todo{Provide a template for what kinds of policy should be implemented like this and template \AppPAL.}

@@

\AppPAL~requires all assertions be made by an explicit speaker.
When translating the policies the author of the policy is generally used as the speaker of the rule (\autoref{tab:principals}),
  with the exception of the HiMSS policy that is written as a contract the user is agreeing to.
All the policies delegate also describe other entities that might also make assertions.
With \AppPAL~policies any speaker can delegate a decision to another speaker (with restrictions on re-delegation).
This might be to a user to acknowledge a policy, or it might be to other groups in the company who are responsible for certain decisions.

@@

Armando~\etal~developed BYODroid as a tool for enforcing BYOD policies through a secure marketplace~\cite{armando_enabling_2014}.
Their tool allows companies to distribute a secure app~store where through a combination of static and dynamic tools they can verify that apps follow fine-grained permission policies.
Their policies are low level, based on ConSpec~\cite{aktug_conspec_2008}, allowing checks based on the JVM state.
Using their tool they implemented parts of a policy relating to personal networks, and data management for the NATO Communications and Information Agency~\cite{armando_developing_2016}.
Their work shows how parts of a BYOD policy can be checked for and enforced using tools.
A \AppPAL~policy might use BYODroid to ensure that a parts of a policy are enforced (as well as other tools for other parts).
\AppPAL~makes explicit how the natural language policy is implemented and by which tools.
